%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[10,letter,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Stefano}{Allesina}


\mobile{+1 773 702 7825}
\email{\href{mailto:sallesina@uchicago.edu}{\nolinkurl{sallesina@uchicago.edu}}}
\homepage{stefanoallesina.github.io}
\googlescholar{14DTOacAAAA}
\researchgate{Stefano-Allesina}
\github{StefanoAllesina}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{soul}
\usepackage[backend=biber]{biblatex}
\usepackage{enumitem}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {September 2024}
    {Stefano Allesina~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\colorlet{awesome}{awesome-emerald}
\colorlet{awesome}{awesome-nephritis}
\colorlet{awesome}{awesome-orange}

\hypertarget{appointments}{%
\section{Appointments}\label{appointments}}

\begin{cventries}
    \cventry{Ecology \& Evolution}{Chair}{University of Chicago}{2021--}{}\vspace{-4.0mm}
    \cventry{Northwestern Institute on Complex Systems}{External faculty}{Northwestern University}{2016--}{}\vspace{-4.0mm}
    \cventry{Ecology \& Evolution}{Professor}{University of Chicago}{2014--}{}\vspace{-4.0mm}
    \cventry{Computation Institute}{Senior Fellow}{University of Chicago}{2014--2018}{}\vspace{-4.0mm}
    \cventry{Ecology \& Evolution and Computation Institute}{Assistant Professor}{University of Chicago}{2009--2014}{}\vspace{-4.0mm}
    \cventry{NCEAS}{Postdoctoral Associate}{U. California, Santa Barbara}{2007--2009}{}\vspace{-4.0mm}
    \cventry{Mercedes Pascual Lab}{Postdoctoral Fellow}{University of Michigan}{2005--2007}{}\vspace{-4.0mm}
    \cventry{Scott Peacor Lab}{Postdoctoral Fellow}{Michigan State U. and NOAA GLERL}{2004--2005}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Ecology}{Ph.D.}{Università degli Studi di Parma, Italy}{2002-2005}{\begin{cvitems}
\item Advisor: Antonio Bodini
\end{cvitems}}
    \cventry{Environmental Sciences}{Laurea}{Università degli Studi di Parma, Italy}{1995-2001}{\begin{cvitems}
\item Advisors: Alessandro Zaccagnini and Antonio Bodini
\end{cvitems}}
\end{cventries}

\hypertarget{published-articles}{%
\section{Published articles}\label{published-articles}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-servan2023effects}{}}%
\CSLLeftMargin{1 }%
\CSLRightInline{Serván, C. A., Capitán, J. A., Miller, Z. R. and
Allesina, S. (2024) Effects of phylogeny on coexistence in model
communities. \ul{The American Naturalist} (accepted).}

\leavevmode\vadjust pre{\hypertarget{ref-lemos2023phylogeny}{}}%
\CSLLeftMargin{2 }%
\CSLRightInline{Lemos-Costa, P., Miller, Z. R. and Allesina, S. (2024)
Phylogeny structures species' interactions in experimental ecological
communities. \ul{Ecology Letters} e14490.}

\leavevmode\vadjust pre{\hypertarget{ref-miller2024coexistence}{}}%
\CSLLeftMargin{3 }%
\CSLRightInline{Miller, Z. R., Clenet, M., Della Libera, K., Massol, F.
and Allesina, S. (2024) Coexistence of many species under a random
competition--colonization trade-off. \ul{Proceedings of the National
Academy of Sciences}, National Acad Sciences 121, e2314215121.}

\leavevmode\vadjust pre{\hypertarget{ref-skwara2023modelling}{}}%
\CSLLeftMargin{4 }%
\CSLRightInline{Skwara, A., Lemos-Costa, P., Miller, Z. R. and Allesina,
S. (2023) Modelling ecological communities when composition is
manipulated experimentally. \ul{Methods in Ecology and Evolution}, Wiley
Online Library 14, 696--707.}

\leavevmode\vadjust pre{\hypertarget{ref-medeiros2023ranking}{}}%
\CSLLeftMargin{5 }%
\CSLRightInline{Medeiros, L. P., Allesina, S., Dakos, V., Sugihara, G.
and Saavedra, S. (2023) Ranking species based on sensitivity to
perturbations under non-equilibrium community dynamics. \ul{Ecology
Letters}, Wiley Online Library 26, 170--183.}

\leavevmode\vadjust pre{\hypertarget{ref-miller2023habitat}{}}%
\CSLLeftMargin{6 }%
\CSLRightInline{Miller, Z. R. and Allesina, S. (2023) Habitat
heterogeneity, environmental feedbacks, and species coexistence across
timescales. \ul{The American Naturalist}, The University of Chicago
Press Chicago, IL 202, E53--E64.}

\leavevmode\vadjust pre{\hypertarget{ref-miller2022no}{}}%
\CSLLeftMargin{7 }%
\CSLRightInline{Miller, Z. R., Lechon-Alonso, P. and Allesina, S. (2022)
No robust multispecies coexistence in a canonical model of plant-soil
feedbacks. \ul{Ecology Letters} 25, 1690--1698.}

\leavevmode\vadjust pre{\hypertarget{ref-de2021local}{}}%
\CSLLeftMargin{8 }%
\CSLRightInline{Castro, F. de, Adl, S. M., Allesina, S., Bardgett, R.
D., Bolger, T., Dalzell, J. J., Emmerson, M., Fleming, T., Garlaschelli,
D., Grilli, J., et al. (2021) Local stability properties of complex,
species-rich soil food webs with functional block structure. \ul{Ecology
and evolution} 11, 16070--16081.}

\leavevmode\vadjust pre{\hypertarget{ref-miller2021metapopulations}{}}%
\CSLLeftMargin{9 }%
\CSLRightInline{Miller, Z.R. and Allesina, S. (2021) Metapopulations
with habitat modification. \ul{Proceedings of the National Academy of
Sciences} 118.}

\leavevmode\vadjust pre{\hypertarget{ref-servan2021tractable}{}}%
\CSLLeftMargin{10 }%
\CSLRightInline{Serván, C.A. and Allesina, S. (2021) Tractable models of
ecological assembly. \ul{Ecology Letters} 24, 1029--1037.}

\leavevmode\vadjust pre{\hypertarget{ref-endpoints}{}}%
\CSLLeftMargin{11 }%
\CSLRightInline{Maynard, D.S., Miller, Z.R. and Allesina, S. (2020)
Predicting coexistence in experimental ecological communities.
\ul{Nature Ecology \& Evolution} 4, 91--100.}

\leavevmode\vadjust pre{\hypertarget{ref-costa2019ecological}{}}%
\CSLLeftMargin{12 }%
\CSLRightInline{Costa, A., González, A. M. M., Guizien, K., Doglioli, A.
M., Gómez, J. M., Petrenko, A. A. and Allesina, S. (2019) Ecological
networks: Pursuing the shortest path, however narrow and crooked.
\ul{Scientific reports} 9, 1--13.}

\leavevmode\vadjust pre{\hypertarget{ref-jovic2019transcriptome}{}}%
\CSLLeftMargin{13 }%
\CSLRightInline{Jovic, K., Grilli, J., Sterken, M. G., Snoek, B. L.,
Riksen, J. A., Allesina, S. and Kammenga, J. E. (2019) Transcriptome
resilience predicts thermotolerance in Caenorhabditis elegans. \ul{BMC
biology} 17, 102.}

\leavevmode\vadjust pre{\hypertarget{ref-quadratic}{}}%
\CSLLeftMargin{14 }%
\CSLRightInline{Maynard, D.S., Wootton, J. T., Serván, C.A. and
Allesina, S. (2019) Reconciling empirical interactions and species
coexistence. \ul{Ecology letters} 22, 1028--1037.}

\leavevmode\vadjust pre{\hypertarget{ref-maynard2019phenotypic}{}}%
\CSLLeftMargin{15 }%
\CSLRightInline{Maynard, D.S., Serván, C.A., Capitán, J. A. and
Allesina, S. (2019) Phenotypic variability promotes diversity and
stability in competitive communities. \ul{Ecology letters} 22,
1776--1786.}

\leavevmode\vadjust pre{\hypertarget{ref-michalska2019telling}{}}%
\CSLLeftMargin{16 }%
\CSLRightInline{Michalska-Smith, M.J. and Allesina, S. (2019) Telling
ecological networks apart by their structure: A computational challenge.
\ul{PLoS computational biology} 15, e1007076.}

\leavevmode\vadjust pre{\hypertarget{ref-chen2019gene}{}}%
\CSLLeftMargin{17 }%
\CSLRightInline{Chen, Y., Shen, Y., Lin, P., Tong, D., Zhao, Y.,
Allesina, S., Shen, X. and Wu, C.-I. (2019) Gene regulatory network
stabilized by pervasive weak repressions: microRNA functions revealed by
the may--wigner theory. \ul{National Science Review} 6, 1176--1188.}

\leavevmode\vadjust pre{\hypertarget{ref-density}{}}%
\CSLLeftMargin{18 }%
\CSLRightInline{Gibbs, T., Grilli, J. and Allesina, S. (2018) Effect of
population abundances on the stability of large random ecosystems.
\ul{Physical Review E} 98.}

\leavevmode\vadjust pre{\hypertarget{ref-spandrels}{}}%
\CSLLeftMargin{19 }%
\CSLRightInline{Maynard, D.S., Serván, C.A. and Allesina, S. (2018)
Network spandrels reflect ecological assembly. \ul{Ecology Letters} 21,
324--334.}

\leavevmode\vadjust pre{\hypertarget{ref-pargroups}{}}%
\CSLLeftMargin{20 }%
\CSLRightInline{Michalska-Smith, M.J., Sander, E.L., Pascual, M. and
Allesina, S. (2018) Understanding the role of parasites in food webs
using the group model. \ul{Journal of Animal Ecology} 87, 790--800.}

\leavevmode\vadjust pre{\hypertarget{ref-randomzoo}{}}%
\CSLLeftMargin{21 }%
\CSLRightInline{Serván, C.A., Capitán, J. A., Grilli, J., Morrison, K.
E. and Allesina, S. (2018) Coexistence of many species in random
ecosystems. \ul{Nature Ecology \& Evolution} 2, 1237.}

\leavevmode\vadjust pre{\hypertarget{ref-diagonal}{}}%
\CSLLeftMargin{22 }%
\CSLRightInline{Barabás, G., Michalska-Smith, M.J. and Allesina, S.
(2017) Self-regulation and the stability of large ecological networks.
\ul{Nature Ecology \& Evolution} 1, 1870.}

\leavevmode\vadjust pre{\hypertarget{ref-namepairs}{}}%
\CSLLeftMargin{23 }%
\CSLRightInline{Grilli, J. and Allesina, S. (2017) Last name analysis of
mobility, gender imbalance, and nepotism across academic systems.
\ul{Proceedings of the National Academy of Sciences of the United States
of America} 114, 7600--7605.}

\leavevmode\vadjust pre{\hypertarget{ref-hoi}{}}%
\CSLLeftMargin{24 }%
\CSLRightInline{Grilli, J., Barabás, G., Michalska-Smith, M.J. and
Allesina, S. (2017) Higher-order interactions stabilize dynamics in
competitive network models. \ul{Nature} 548, 210--213.}

\leavevmode\vadjust pre{\hypertarget{ref-feasibility}{}}%
\CSLLeftMargin{25 }%
\CSLRightInline{Grilli, J., Adorisio, M., Suweis, S., Barabás, G.,
Banavar, J. R., Allesina, S. and Maritan, A. (2017) Feasibility and
coexistence of large ecological communities. \ul{Nature Communications}
8, 14389.}

\leavevmode\vadjust pre{\hypertarget{ref-reviewcoex}{}}%
\CSLLeftMargin{26 }%
\CSLRightInline{Levine, J. M., Bascompte, J., Adler, P. and Allesina, S.
(2017) Beyond pairwise coexistence: Biodiversity maintenance in complex
ecological communities. \ul{Nature} 546, 3376--3386.}

\leavevmode\vadjust pre{\hypertarget{ref-worms}{}}%
\CSLLeftMargin{27 }%
\CSLRightInline{Jovic, K., Sterken, M. G., Grilli, J., Bevers, R. P. J.,
Rodriguez, M., Riksen, J. A. G., Allesina, S., Kammenga, J. E. and
Snoek, L. B. (2017) Temporal dynamics of gene expression in
heat-stressed caenorhabditis elegans. \ul{PLoS ONE} 12.}

\leavevmode\vadjust pre{\hypertarget{ref-laura}{}}%
\CSLLeftMargin{28 }%
\CSLRightInline{Dee, L. E., Allesina, S., Bonn, A., Eklöf, A., Gaines,
S. D., Hines, J., Jacob, U., McDonald-Madden, E., Possingham, H.,
Schröter, M., et al. (2017) Operationalizing network theory for
ecosystem service assessments. \ul{Trends in Ecology \& Evolution} 32,
118--130.}

\leavevmode\vadjust pre{\hypertarget{ref-productivity}{}}%
\CSLLeftMargin{29 }%
\CSLRightInline{Michalska-Smith, M.J. and Allesina, S. (2017) And, not
Or: Quality, quantity in scientific publishing. \ul{PLoS One} 12,
e0178074.}

\leavevmode\vadjust pre{\hypertarget{ref-lizbayes}{}}%
\CSLLeftMargin{30 }%
\CSLRightInline{Sander, E.L., Wootton, J. T. and Allesina, S. (2017)
Ecological network inference from long-term presence-absence data.
\ul{Scientific reports} 7, 7154.}

\leavevmode\vadjust pre{\hypertarget{ref-intrainter}{}}%
\CSLLeftMargin{31 }%
\CSLRightInline{Barabás, G., Smith, M.J. and Allesina, S. (2016) The
effect of intra- and interspecific competition on coexistence in
multispecies communities. \ul{American Naturalist} 188, E1--E12.}

\leavevmode\vadjust pre{\hypertarget{ref-song}{}}%
\CSLLeftMargin{32 }%
\CSLRightInline{Masco, C., Allesina, S., Mennill, D. J. and
Pruett-Jones, S. (2016) Song overlapping: Distinguishing between
intention and chance. \ul{Bioacoustics} 25, 29--40.}

\leavevmode\vadjust pre{\hypertarget{ref-modularityquaternions}{}}%
\CSLLeftMargin{33 }%
\CSLRightInline{Grilli, J., Rogers, T. and Allesina, S. (2016)
Modularity and stability in ecological communities. \ul{Nature
Communications} 7, 12031+.}

\leavevmode\vadjust pre{\hypertarget{ref-Sophie}{}}%
\CSLLeftMargin{34 }%
\CSLRightInline{McCoy, S. J., Pfister, C. A. and Allesina, S. (2016)
Ocean acidification affects competition for space: Projections of
community structure using cellular automata. \ul{Proceedings of the
Royal Society B: Biological Sciences} 283, 20152561.}

\leavevmode\vadjust pre{\hypertarget{ref-eyeball}{}}%
\CSLLeftMargin{35 }%
\CSLRightInline{Allesina, S., Grilli, J., Barabás, G., Tang, S.,
Aljadeff, J. and Maritan, A. (2015) Predicting the stability of large
structured food webs. \ul{Nature Communications} 6, 7842.}

\leavevmode\vadjust pre{\hypertarget{ref-Japan}{}}%
\CSLLeftMargin{36 }%
\CSLRightInline{Allesina, S. and Tang, S. (2015) The
stability-complexity relationship at age 40: A random matrix
perspective. \ul{Population Ecology} 57, 63--75.}

\leavevmode\vadjust pre{\hypertarget{ref-binning}{}}%
\CSLLeftMargin{37 }%
\CSLRightInline{Barabás, G. and Allesina, S. (2015) Predicting global
community properties from uncertain estimates of interaction strengths.
\ul{Journal of the Royal Society Interface} 12, 20150218.}

\leavevmode\vadjust pre{\hypertarget{ref-metapop}{}}%
\CSLLeftMargin{38 }%
\CSLRightInline{Grilli, J., Barabás, G. and Allesina, S. (2015)
Metapopulation persistence in random fragmented landscapes. \ul{PLoS
Computational Biology} 11, e1004251.}

\leavevmode\vadjust pre{\hypertarget{ref-Jon}{}}%
\CSLLeftMargin{39 }%
\CSLRightInline{Borrelli, J. J., Allesina, S., Amarasekare, P., Arditi,
R., Chase, I., Damuth, J., Ginzburg, L., Holt, R. D., Logofet, D. O.,
Novak, M., et al. (2015) Selection on stability across ecological
scales. \ul{Trends in Ecology \& Evolution} 30, 417--425.}

\leavevmode\vadjust pre{\hypertarget{ref-samir}{}}%
\CSLLeftMargin{40 }%
\CSLRightInline{Suweis, S., Grilli, J., Banavar, J., Allesina, S. and
Maritan, A. (2015) Effect of localization on the stability of
mutualistic ecological networks. \ul{Nature Communications} 6, 10179+.}

\leavevmode\vadjust pre{\hypertarget{ref-signgroup}{}}%
\CSLLeftMargin{41 }%
\CSLRightInline{Sander, S., Wootton, J. T. and Allesina, S. (2015) What
can interaction webs tell us about species roles? \ul{PLoS Computational
Biology} 11, e10043330.}

\leavevmode\vadjust pre{\hypertarget{ref-neutelcomment}{}}%
\CSLLeftMargin{42 }%
\CSLRightInline{Smith, M.J., Sander, S., Barabás, G. and Allesina, S.
(2015) Stability and feedback levels in food web models. \ul{Ecology
Letters} 18, 593--595.}

\leavevmode\vadjust pre{\hypertarget{ref-Abstracts}{}}%
\CSLLeftMargin{43 }%
\CSLRightInline{Weinberger, C.J., Evans, J. A. and Allesina, S. (2015)
Ten simple (empirical) rules for writing science. \ul{PLoS Computational
Biology} 11, e1004205.}

\leavevmode\vadjust pre{\hypertarget{ref-Lizzie}{}}%
\CSLLeftMargin{44 }%
\CSLRightInline{Wolkovich, E. M., Allesina, S., Cottingham, K. L.,
Moore, J. C., Sandin, S. A. and Mazancourt, C. de. (2014) Linking the
green and brown worlds: The prevalence and effect of multi-channel
feeding in food webs. \ul{Ecology} 95, 3376--3386.}

\leavevmode\vadjust pre{\hypertarget{ref-Countrycit}{}}%
\CSLLeftMargin{45 }%
\CSLRightInline{Smith, M.J., Weinberger, C., Bruna, E. and Allesina, S.
(2014) The Scientific Impact of nations: Journal Placement and Citation
Performance. \ul{PLoS ONE} 9, e109195.}

\leavevmode\vadjust pre{\hypertarget{ref-GBU}{}}%
\CSLLeftMargin{46 }%
\CSLRightInline{Staniczenko, P.P.A., Smith, M.J. and Allesina, S. (2014)
Selecting food web models using normalised maximum likelihood.
\ul{Methods in Ecology and Evolution} 5, 551--562.}

\leavevmode\vadjust pre{\hypertarget{ref-Reactivity}{}}%
\CSLLeftMargin{47 }%
\CSLRightInline{Tang, S. and Allesina, S. (2014) Reactivity and
stability of large ecosystems. \ul{Frontiers in Ecology and Evolution}
2, art no. 21.}

\leavevmode\vadjust pre{\hypertarget{ref-Stability2}{}}%
\CSLLeftMargin{48 }%
\CSLRightInline{Tang, S., Pawar, S. and Allesina, S. (2014) Correlation
between interaction strengths drives stability in large ecological
networks. \ul{Ecology Letters} 17, 1094--1100.}

\leavevmode\vadjust pre{\hypertarget{ref-Chris2}{}}%
\CSLLeftMargin{49 }%
\CSLRightInline{Lortie, C. J., Allesina, S., Aarssen, L., Grod, O. and
Budden, A. E. (2013) With great power comes great responsibility: The
importance of rejection, power, and editors in the practice of
scientific publishing. \ul{PLoS One} 8, e85382.}

\leavevmode\vadjust pre{\hypertarget{ref-BayesNet}{}}%
\CSLLeftMargin{50 }%
\CSLRightInline{Eklöf, A., Tang, S. and Allesina, S. (2013) Secondary
extinctions in food webs: A Bayesian network approach. \ul{Methods in
Ecology and Evolution} 4, 760--770.}

\leavevmode\vadjust pre{\hypertarget{ref-Dimensions}{}}%
\CSLLeftMargin{51 }%
\CSLRightInline{Eklöf, A., Jacob, U., Kopp, J.C., Bosch, J.,
Castro-Urgal, R., Chacoff, N. P., Dalsgaard, B., Sassi, C. de, Galetti,
M., Guimãrares Jr., P. R., et al. (2013) The dimensionality of
ecological networks. \ul{Ecology Letters} 16, 577--583.}

\leavevmode\vadjust pre{\hypertarget{ref-John2}{}}%
\CSLLeftMargin{52 }%
\CSLRightInline{Parker, J. N., Lortie, C. and Allesina, S. (2013)
Characterizing a scientific elite (b): Publication and citation patterns
of the most highly cited scientists in environmental science and
ecology. \ul{Scientometrics} 94, 469--480.}

\leavevmode\vadjust pre{\hypertarget{ref-Nestedness}{}}%
\CSLLeftMargin{53 }%
\CSLRightInline{Staniczenko, P.P.A., Kopp, J.C. and Allesina, S. (2013)
The ghost of nestedness in ecological networks. \ul{Nature
Communications} 4, 1391.}

\leavevmode\vadjust pre{\hypertarget{ref-BodiniCities}{}}%
\CSLLeftMargin{54 }%
\CSLRightInline{Bodini, A., Bondavalli, C. and Allesina, S. (2012)
Cities as ecosystems: Growth, development and implications for
sustainability. \ul{Ecological Modelling} 245, 185--198.}

\leavevmode\vadjust pre{\hypertarget{ref-Cities2}{}}%
\CSLLeftMargin{55 }%
\CSLRightInline{Bodini, A., Bondavalli, C. and Allesina,S. (2012) Cities
as ecosystems: Functional similarities and the quest for sustainability.
\ul{Developments in Environmental Modelling} 25, 297--318.}

\leavevmode\vadjust pre{\hypertarget{ref-Ana}{}}%
\CSLLeftMargin{56 }%
\CSLRightInline{Martin-González, A. M., Allesina, S., Rodrigo, A. and
Bosch, J. (2012) Drivers of compartmentalization in a Mediterranean
pollination network. \ul{Oikos} 121, 2001--2013.}

\leavevmode\vadjust pre{\hypertarget{ref-NewsAndViews}{}}%
\CSLLeftMargin{57 }%
\CSLRightInline{Allesina, S. (2012) Ecology: The more the merrier --
News \& Views. \ul{Nature} 487, 175--176.}

\leavevmode\vadjust pre{\hypertarget{ref-PeerReview}{}}%
\CSLLeftMargin{58 }%
\CSLRightInline{Allesina, S. (2012) Modeling peer review: An agent-based
approach. \ul{Ideas in Ecology and Evolution} 5, 27--35.}

\leavevmode\vadjust pre{\hypertarget{ref-StabilityCriteria}{}}%
\CSLLeftMargin{59 }%
\CSLRightInline{Allesina, S. and Tang, S. (2012) Stability criteria for
complex ecosystems. \ul{Nature} 483, 205--208.}

\leavevmode\vadjust pre{\hypertarget{ref-Chris}{}}%
\CSLLeftMargin{60 }%
\CSLRightInline{Lortie, C. J., Aarssen, L., Parker, J. P. and Allesina,
S. (2012) Good news for the people who love bad news: An analysis of the
funding of the top 1\% most highly cited ecologists. \ul{Oikos} 121,
1005--1008.}

\leavevmode\vadjust pre{\hypertarget{ref-CarlosSex}{}}%
\CSLLeftMargin{61 }%
\CSLRightInline{Melián, C. J., Alonso, D., Allesina, S., Condit, R. S.
and Etienne, R. S. (2012) Does sex speed up evolutionary rate and
increase biodiversity? \ul{PLoS Computational Biology} 8, e1002414.}

\leavevmode\vadjust pre{\hypertarget{ref-Konrad}{}}%
\CSLLeftMargin{62 }%
\CSLRightInline{Acuna, D. E., Allesina, S. and Kording, K. P. (2012)
Future impact: Predicting scientific success. \ul{Nature} 489,
201--202.}

\leavevmode\vadjust pre{\hypertarget{ref-Taxonomy}{}}%
\CSLLeftMargin{63 }%
\CSLRightInline{Eklöf, A., Helmus, M., Moore, M and Allesina, S. (2012)
Relevance of evolutionary history for food web structure.
\ul{Proceedings of the Royal Society B: Biological Sciences} 279,
1588--1596.}

\leavevmode\vadjust pre{\hypertarget{ref-ADBM}{}}%
\CSLLeftMargin{64 }%
\CSLRightInline{Allesina, S. (2011) Predicting trophic relations in
ecological networks: A test of the Allometric Diet Breadth Model.
\ul{Journal of Theoretical Biology} 279, 161--168.}

\leavevmode\vadjust pre{\hypertarget{ref-Nepotism}{}}%
\CSLLeftMargin{65 }%
\CSLRightInline{Allesina, S. (2011) Measuring nepotism through shared
last names: The case of Italian academia. \ul{PLoS ONE} 6, e21160.}

\leavevmode\vadjust pre{\hypertarget{ref-Ferrarini}{}}%
\CSLLeftMargin{66 }%
\CSLRightInline{Allesina, S. and Levine, J. M. (2011) Reply to
Ferrarini: Strengths and weaknesses of simple competition models.
\ul{Proceedings of the National Academy of Sciences of the United States
of America} 108, E346.}

\leavevmode\vadjust pre{\hypertarget{ref-RPS}{}}%
\CSLLeftMargin{67 }%
\CSLRightInline{Allesina, S. and Levine, J. M. (2011) A competitive
network theory of species diversity. \ul{Proceedings of the National
Academy of Sciences of the United States of America} 108, 5638--5642.}

\leavevmode\vadjust pre{\hypertarget{ref-Seregenti}{}}%
\CSLLeftMargin{68 }%
\CSLRightInline{Baskerville, E. B., Dobson, A. P., Bedford, T.,
Allesina, S., Anderson, T. M. and Pascual, M. (2011) Spatial guilds in
the Serengeti food web revealed by a Bayesian group model. \ul{PLoS
Computational Biology} 7, e1002321.}

\leavevmode\vadjust pre{\hypertarget{ref-JOSE}{}}%
\CSLLeftMargin{69 }%
\CSLRightInline{Rojas-Echenique, J. and Allesina, S. (2011) Interaction
rules affect species coexistence in intransitive networks. \ul{Ecology}
92, 1174--1180.}

\leavevmode\vadjust pre{\hypertarget{ref-Alex}{}}%
\CSLLeftMargin{70 }%
\CSLRightInline{Zook, A.E., Eklöf, A., Jacob, U. and Allesina, S. (2011)
Food webs: Ordering species according to body size yields high degree of
intervality. \ul{Journal of Theoretical Biology} 271, 106--113.}

\leavevmode\vadjust pre{\hypertarget{ref-Daria}{}}%
\CSLLeftMargin{71 }%
\CSLRightInline{Allesina, S., Azzi, A., Battini, D. and Regattieri, A.
(2010) Performance measurement in supply chains: New network analysis
and entropic indexes. \ul{International Journal of Production Research}
48, 2297--2321.}

\leavevmode\vadjust pre{\hypertarget{ref-Carlos}{}}%
\CSLLeftMargin{72 }%
\CSLRightInline{Melián, C. J., Alonso, D., Vázquez, D. P., Regetz, J.
and Allesina, S. (2010) Frequency-dependent selection predicts patterns
of radiations and biodiversity. \ul{PLoS Computational Biology} 6,
e1000892.}

\leavevmode\vadjust pre{\hypertarget{ref-John}{}}%
\CSLLeftMargin{73 }%
\CSLRightInline{Parker, J. N., Lortie, C. and Allesina, S. (2010)
Characterizing a scientific elite: The social characteristics of the
most highly cited scientists in environmental science and ecology.
\ul{Scientometrics} 85, 129--143.}

\leavevmode\vadjust pre{\hypertarget{ref-Catching}{}}%
\CSLLeftMargin{74 }%
\CSLRightInline{Bodini, A., Bellingeri, M., Allesina, S. and Bondavalli,
C. (2009) Using food web dominator trees to catch secondary extinctions
in action. \ul{Philosophical Transactions of the Royal Society B:
Biological Sciences} 364, 1725--1731.}

\leavevmode\vadjust pre{\hypertarget{ref-Andy}{}}%
\CSLLeftMargin{75 }%
\CSLRightInline{Dobson, A., Allesina, S., Lafferty, K. and Pascual, M.
(2009) The assembly, collapse and restoration of food webs.
\ul{Philosophical Transactions of the Royal Society B: Biological
Sciences} 364, 1803--1806.}

\leavevmode\vadjust pre{\hypertarget{ref-Redundant}{}}%
\CSLLeftMargin{76 }%
\CSLRightInline{Allesina, S., Bodini, A. and Pascual, M. (2009)
Functional links and robustness in food webs. \ul{Philosophical
Transactions of the Royal Society B: Biological Sciences} 364,
1701--1709.}

\leavevmode\vadjust pre{\hypertarget{ref-Google}{}}%
\CSLLeftMargin{77 }%
\CSLRightInline{Allesina, S. and Pascual, M. (2009) Googling food webs:
Can an eigenvector measure species' importance for coextinctions?
\ul{PLoS Computational Biology} 5, e1000494.}

\leavevmode\vadjust pre{\hypertarget{ref-Groups}{}}%
\CSLLeftMargin{78 }%
\CSLRightInline{Allesina, S. and Pascual, M. (2009) Food web models: A
plea for groups. \ul{Ecology Letters} 12, 652--662.}

\leavevmode\vadjust pre{\hypertarget{ref-Marco}{}}%
\CSLLeftMargin{79 }%
\CSLRightInline{Scotti, M., Bondavalli, C., Bodini, A. and Allesina, S.
(2009) Using trophic hierarchy to understand food web structure.
\ul{Oikos} 118, 1695--1702.}

\leavevmode\vadjust pre{\hypertarget{ref-Science08}{}}%
\CSLLeftMargin{80 }%
\CSLRightInline{Allesina, S., Alonso, D. and Pascual, M. (2008) A
general model for food web structure. \ul{Science} 320, 658--661.}

\leavevmode\vadjust pre{\hypertarget{ref-PredPrey}{}}%
\CSLLeftMargin{81 }%
\CSLRightInline{Allesina, S. and Pascual, M. (2008) Network structure,
predator-prey modules, and stability in large food webs. \ul{Theoretical
Ecology} 1, 55--64.}

\leavevmode\vadjust pre{\hypertarget{ref-Kevin}{}}%
\CSLLeftMargin{82 }%
\CSLRightInline{Lafferty, K. D., Allesina, S., Arim, M., Briggs, C. J.,
De Leo, G., Dobson, A. P., Dunne, J. A., Johnson, P. T. J., Kuris, A.
M., Marcogliese, D. J., et al. (2008) Parasites in food webs: The
ultimate missing links. \ul{Ecology Letters} 11, 533--546.}

\leavevmode\vadjust pre{\hypertarget{ref-battini2007towards}{}}%
\CSLLeftMargin{83 }%
\CSLRightInline{Battini, D., Persona, A. and Allesina, S. (2007) Towards
a use of network analysis: Quantifying the complexity of supply chain
networks. \ul{International Journal of Electronic Customer Relationship
Management} 1, 75--90.}

\leavevmode\vadjust pre{\hypertarget{ref-Dove2}{}}%
\CSLLeftMargin{84 }%
\CSLRightInline{Peacor, S. D., Allesina, S., Riolo, R. L. and Hunter, T.
S. (2007) A new computational system, DOVE (digital organisms in a
virtual ecosystem), to study phenotypic plasticity and its effects in
food webs. \ul{Ecological Modelling} 205, 13--28.}

\leavevmode\vadjust pre{\hypertarget{ref-Bottle}{}}%
\CSLLeftMargin{85 }%
\CSLRightInline{Allesina, S., Bodini, A. and Bondavalli, C. (2006)
Secondary extinctions in ecological networks: Bottlenecks unveiled.
\ul{Ecological Modelling} 194, 150--161.}

\leavevmode\vadjust pre{\hypertarget{ref-Santo}{}}%
\CSLLeftMargin{86 }%
\CSLRightInline{Bondavalli, C., Bodini, A., Rossetti, G. and Allesina,
S. (2006) Detecting stress at the whole-ecosystem level: The case of a
mountain lake (Lake Santo, Italy). \ul{Ecosystems} 9, 768--787.}

\leavevmode\vadjust pre{\hypertarget{ref-Marco2}{}}%
\CSLLeftMargin{87 }%
\CSLRightInline{Scotti, M., Allesina, S., Bondavalli, C., Bodini, A. and
Abarca-Arenas, L. G. (2006) Effective trophic positions in ecological
acyclic networks. \ul{Ecological Modelling} 198, 495--505.}

\leavevmode\vadjust pre{\hypertarget{ref-Dove}{}}%
\CSLLeftMargin{88 }%
\CSLRightInline{Peacor, S. D., Allesina, S., Riolo, R. L. and Pascual,
M. (2006) Phenotypic plasticity opposes species invasions by altering
fitness surface. \ul{PLoS Biology} 4, 2112--2120.}

\leavevmode\vadjust pre{\hypertarget{ref-ScalingRevis}{}}%
\CSLLeftMargin{89 }%
\CSLRightInline{Allesina, S. and Bodini, A. (2005) Food web networks:
Scaling relation revisited. \ul{Ecological Complexity} 2, 323--338.}

\leavevmode\vadjust pre{\hypertarget{ref-SCC}{}}%
\CSLLeftMargin{90 }%
\CSLRightInline{Allesina, S., Bodini, A. and Bondavalli, C. (2005)
Ecological subsystems via graph theory: The role of strongly connected
components. \ul{Oikos} 110, 164--176.}

\leavevmode\vadjust pre{\hypertarget{ref-Aggregation}{}}%
\CSLLeftMargin{91 }%
\CSLRightInline{Allesina, S., Bondavalli, C. and Scharler, U. M. (2005)
The consequences of the aggregation of detritus pools in ecological
networks. \ul{Ecological Modelling} 189, 221--232.}

\leavevmode\vadjust pre{\hypertarget{ref-Dominators}{}}%
\CSLLeftMargin{92 }%
\CSLRightInline{Allesina, S. and Bodini, A. (2004) Who dominates whom in
the ecosystem? Energy flow bottlenecks and cascading extinctions.
\ul{Journal of Theoretical Biology} 230, 351--358.}

\leavevmode\vadjust pre{\hypertarget{ref-WAND}{}}%
\CSLLeftMargin{93 }%
\CSLRightInline{Allesina, S. and Bondavalli, C. (2004) WAND: An
ecological network analysis user-friendly tool. \ul{Environmental
Modelling and Software} 19, 337--340.}

\leavevmode\vadjust pre{\hypertarget{ref-Cycling}{}}%
\CSLLeftMargin{94 }%
\CSLRightInline{Allesina, S. and Ulanowicz, R. E. (2004) Cycling in
ecological networks: Finn's index revisited. \ul{Computational Biology
and Chemistry} 28, 227--233.}

\leavevmode\vadjust pre{\hypertarget{ref-Balance}{}}%
\CSLLeftMargin{95 }%
\CSLRightInline{Allesina, S. and Bondavalli, C. (2003) Steady state of
ecosystem flow networks: A comparison between balancing procedures.
\ul{Ecological Modelling} 165, 221--229.}

\hypertarget{preprints}{%
\section{Preprints}\label{preprints}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-allesina2021intraspecific}{}}%
\CSLLeftMargin{1 }%
\CSLRightInline{Allesina, S., Miller, Z.R. and Serván, C.A. (2021)
Intraspecific variation stabilizes classic predator-prey dynamics.
\ul{bioRxiv}, Cold Spring Harbor Laboratory.}

\leavevmode\vadjust pre{\hypertarget{ref-Superellipse}{}}%
\CSLLeftMargin{2 }%
\CSLRightInline{Allesina, S., Sander, E., Smith, M.J. and Tang, S.
(2013) Superelliptical laws for complex networks. \ul{arXiv}.}

\leavevmode\vadjust pre{\hypertarget{ref-NepotismResponse}{}}%
\CSLLeftMargin{3 }%
\CSLRightInline{Allesina, S. (2012) Measuring nepotism through shared
last names: Response to Ferlazzo and Sdoia. \ul{arXiv}.}

\hypertarget{books-book-reviews-chapters}{%
\section{Books, book reviews \&
chapters}\label{books-book-reviews-chapters}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-allesina2020going}{}}%
\CSLLeftMargin{1 }%
\CSLRightInline{Allesina, S. (2020) Going big. In Unsolved problems in
ecology (Dobson, A., Tilman, D., and Holt, R. D., eds.), pp 374--379,
Princeton University Press.}

\leavevmode\vadjust pre{\hypertarget{ref-theorecolch6}{}}%
\CSLLeftMargin{2 }%
\CSLRightInline{Allesina, S. and Grilli, J. (2020) Models for large
ecological communities---a random matrix approach. In Theoretical
ecology: Concepts and applications (McCann, K. S., and Gellner, G.,
eds.), pp 74--92, Oxford University Press.}

\leavevmode\vadjust pre{\hypertarget{ref-CSB}{}}%
\CSLLeftMargin{3 }%
\CSLRightInline{Allesina, S. and Wilmes, M. (2019) Computing skills for
biologists --- a toolbox, Princeton University Press, Princeton, NJ.}

\leavevmode\vadjust pre{\hypertarget{ref-BookReview2}{}}%
\CSLLeftMargin{4 }%
\CSLRightInline{Allesina, S. (2013) Food web stability, unapologetically
-- Book review. \ul{Ecology} 94, 2114--2115.}

\leavevmode\vadjust pre{\hypertarget{ref-librobo}{}}%
\CSLLeftMargin{5 }%
\CSLRightInline{Bodini, A., Allesina, S. and Bondavalli, C. (2012)
Network science in ecology: The structure of ecological communities and
the biodiversity question, pp 220--236.}

\leavevmode\vadjust pre{\hypertarget{ref-AllesinaEklof}{}}%
\CSLLeftMargin{6 }%
\CSLRightInline{Eklöf, A. and Allesina, S. (2012) Ecological networks.
In Encyclopedia of theoretical ecology (Hastings, A., and Gross, L.,
eds.), pp 470--478, U. California Press, Berkeley, CA.}

\leavevmode\vadjust pre{\hypertarget{ref-BookReview}{}}%
\CSLLeftMargin{7 }%
\CSLRightInline{Allesina, S. (2009) Learning R the practical way -- Book
review. \ul{Ecology} 90, 2335--2336.}

\leavevmode\vadjust pre{\hypertarget{ref-Allesina2008812}{}}%
\CSLLeftMargin{8 }%
\CSLRightInline{Allesina, S. (2008) Cycling and cycling indices. In
Encyclopedia of ecology (Jorgensen, S. E., and Fath, B., eds.), pp
812--819, Academic Press, Oxford.}

\leavevmode\vadjust pre{\hypertarget{ref-Allesina2008254}{}}%
\CSLLeftMargin{9 }%
\CSLRightInline{Allesina, S. and Bodini, A. (2008) Ascendency. In
Encyclopedia of ecology (Jorgensen, S. E., and Fath, B., eds.), pp
254--263, Academic Press, Oxford.}

\leavevmode\vadjust pre{\hypertarget{ref-Libro}{}}%
\CSLLeftMargin{10 }%
\CSLRightInline{Bodini, A., Bondavalli, C. and Allesina, S. (2007)
L'ecosistema e le sue relazioni. Idee e strumenti per la valutazione di
impatto e ambientale e di incidenza., Franco Angeli, Milan.}

\hypertarget{support}{%
\section{Support}\label{support}}

\begin{cventries}
    \cventry{Revisiting the relationship between phylogenetic diversity and productivity DEB \#2022742}{National Science Foundation}{\$449,295}{10/20 – 10/23}{\begin{cvitems}
\item PI: Allesina
\end{cvitems}}
    \cventry{Quantitative and Statistical Thinking in the Life Sciences: Quantitative Biology Fellowships}{Burroughs Wellcome Fund Foundation}{\$150,000}{10/10 – 10/20}{\begin{cvitems}
\item PI: Allesina, five Co-PIs
\end{cvitems}}
    \cventry{Reproducibility and Rigor in Quantitative Biology: A Hands-on Approach NRT \#1734818}{National Science Foundation}{\$499,259}{9/17 – 8/21}{\begin{cvitems}
\item PI: Prince, Co-PI Allesina \& Palmer
\end{cvitems}}
    \cventry{Crossing the ultimate tipping point: predicting death in C. elegans}{Human Frontier Science Program}{\$750,000}{12/14 – 12/18}{\begin{cvitems}
\item PI: Kammenga \& Allesina
\end{cvitems}}
    \cventry{Spectral Characterization of Ecological Networks}{FACCTS U. Chicago}{\$8,000}{2/14 – 2/15}{\begin{cvitems}
\item PI: Allesina \& Thébault.
\end{cvitems}}
    \cventry{CAREER: Scientific Computing for a New Generation of Ecologists DEB \#1148867}{National Science Foundation}{\$599,244}{9/12 – 8/18}{\begin{cvitems}
\item PI: Allesina
\end{cvitems}}
    \cventry{Bacteria test biodiversity theories}{James S. McDonnell Foundation}{\$449,817}{8/10 – 7/14}{\begin{cvitems}
\item PI: Allesina Co-PI: Bergelson
\end{cvitems}}
    \cventry{Accelerating the pace of discovery by changing the peer review algorithm SBE EAGER \#1042164}{National Science Foundation}{\$240,073}{8/10 – 7/14}{\begin{cvitems}
\item PI: Allesina
\end{cvitems}}
    \cventry{The Spider and the Web: inference in ecological networks EF \#0827493}{National Science Foundation}{\$636,000}{9/08 – 8/14}{\begin{cvitems}
\item PI: Pascual Co-PI: Allesina
\end{cvitems}}
\end{cventries}

\hypertarget{mentoring}{%
\section{Mentoring}\label{mentoring}}

\hypertarget{graduate-students}{%
\subsection{Graduate students}\label{graduate-students}}

Si Tang (2010-2013), Elizabeth Sander (2012-2017) (with J.T. Wootton),
Matthew Michalska-Smith (2013-2018), Carlos Marcelo Serván (2016-2020),
Zach Miller (2017-2022), Pablo Lechon-Alonso (2021-)

\hypertarget{postdocs}{%
\subsection{Postdocs}\label{postdocs}}

Anna Eklöf (2010-2012), Phillip Staniczenko (2011-2013), Samraat Pawar
(2012-2013), György Barabás (2014-2016), Madlen Wilmes (2015), Jacopo
Grilli (2015-2017), Daniel Maynard (2017-2019), Srilena Kundu
(2022-2024), Paula Lemos-Costa (2019-)

\hypertarget{undergraduatepredoctoral}{%
\subsection{Undergraduate/predoctoral}\label{undergraduatepredoctoral}}

Jose Rojas (2009-2010), Alex Zook (2009-2010), Philip Reinhold
(2010-2011), M Moore (2010-2011), Jason Kopp (2011-2012), Matthew Smith
(2012-2013), Michael Begun (2012-2013), Cody Weinberger (2013-2015),
Theo Gibbs (2016-2018), Kevin Trickey (2017), Abby Skwara (2019-2021)

\hypertarget{awards-membership}{%
\section{Awards \& Membership}\label{awards-membership}}

\begin{itemize}
\tightlist
\item
  U. Chicago Biological Sciences Division, Distinguished Investigator
  Award (2018).
\item
  NSF CAREER Award (2012).
\item
  NCEAS postdoctoral associate (2007, 2 years of support).
\item
  Italian Ministry of University - PhD Scholarship (2002, 3 years of
  support).
\item
  International Society for Ecological Modeling young researcher bursary
  (2004).
\item
  Member of the Ecological Society of America (starting 2005).
\item
  Member of the British Ecological Society (starting 2010).
\end{itemize}

\hypertarget{service-and-leadership}{%
\section{Service and leadership}\label{service-and-leadership}}

\hypertarget{university-of-chicago}{%
\subsection{University of Chicago}\label{university-of-chicago}}

\begin{itemize}
\tightlist
\item
  College Council (nominated) and Committee of the College Council
  (elected), 2024-
\item
  Committee on Future Academic Directions in Climate and Energy,
  advising President Alivisatos and Provost Lee, 2022
\item
  Chair, Ecology \& Evolution, 2021-
\item
  Director of Graduate Studies, Ecology \& Evoltuion, 2014-2021
\item
  Committee on Promotion and Tenure, 2015-2020
\item
  Committee on Assistant Professors, 2014-2015
\end{itemize}

\hypertarget{editor}{%
\subsection{Editor}\label{editor}}

\begin{itemize}
\tightlist
\item
  PLoS Computational Biology, Guest Editor (2012-2015), Associate Editor
  (2015-2017), Deputy Editor (2017-2021)
\item
  Guest Editor for PNAS (2018), eLife (2015)
\item
  Scientific Reports, Editor (2015-2017)
\item
  Journal of Complex Networks, Associate Editor (2012-2017)
\item
  Faculty of 1000, Population Ecology, 2011-2016
\item
  Oikos, Subject Editor, 2009-2017
\end{itemize}

\hypertarget{reviewer}{%
\subsection{Reviewer}\label{reviewer}}

American Naturalist; Basic and Applied Ecology; Behavioral Ecology;
Biological Reviews; Biology Letters; BioScience; Branco Weiss
Fellowship; Briefings in Bioinformatics; Chaos; Ecography; Ecological
Complexity; Ecological Engineering; Ecological Indicators; Ecological
Modelling; Ecological Monographs; Ecology; Ecology Letters;
Environmental Modelling \& Assessment; Environmental Modelling \&
Software; Estuarine, Coastal and Shelf Science; European Physical
Journal B; European Research Council; Fisheries Research; Global Ecology
and Biogeography; Journal of Animal Ecology; Journal of Mathematical
Biology; Journal of Robust and Nonlinear Control; Journal of the
Association for Information Science and Technology; Journal of
Theoretical Biology; Journal of the Royal Society Interface; Marine
Ecology Progress Series; Marsden Fund -- Royal Society of New Zealand;
Methods in Ecology \& Evolution; Microsoft Research; National Science
Foundation; Nature; Nature Communications; Nature Ecology \& Evolution;
Nature Methods; Nature Physics; NERC; Oikos; Philosophical Transactions
of the Royal Society Series B; Physical Reviews E; Physical Reviews X;
Physics Letters A; PLoS Biology; PLoS Computational Biology; PLoS One;
Proceedings of the National Academy of Sciences USA; Proceedings of the
Royal Society Series B; Revue canadienne des sciences de l'information
et de bibliotheconomie; Science; Science Advances; Scientometrics;
Sinauer Publishing; The Social Science Journal; The Lancet Global
Health; Theoretical Ecology; Theoretical Population Biology; The
Quarterly Review of Biology; Romanian National Council for Scientific
Research; Scientific Reports; Trends in Ecology \& Evolution; Trends in
Parasitology; U. California Press; U. Chicago Press; U. Nebraska Omaha
Internal Funding.

\hypertarget{panelist}{%
\subsection{Panelist}\label{panelist}}

National Science Foundation (EF 2010, GRFP 2016)

\hypertarget{organizer}{%
\subsection{Organizer}\label{organizer}}

\begin{itemize}
\tightlist
\item
  BSD Boot Camp on Quantitative Biology (S. Allesina, S. Palmer and V.
  Prince) 2015-2019
\item
  A primer in ecological networks: theory \& data (A. Bodini, G. DeLeo,
  S. Allesina \& C. Bondavalli) 2008
\end{itemize}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\begin{cventries}
    \cventry{Theoretical Community Ecology}{Graduate}{2021--}{Allesina}{}\vspace{-4.0mm}
    \cventry{Fundamentals of Biological Data Analysis}{Undergraduate}{2018--}{Allesina \& Kondrashov}{}\vspace{-4.0mm}
    \cventry{Computing Skills for Biologists}{Graduate}{2012--2020}{Allesina}{}\vspace{-4.0mm}
    \cventry{How can we understand the biosphere?}{Undergraduate}{2016--2018}{Allesina \& Kronforst}{}\vspace{-4.0mm}
    \cventry{Evolution \& Ecology}{Undergraduate}{2009--2015}{Allesina \& Coyne; Allesina \& Kronforst}{}\vspace{-4.0mm}
    \cventry{Theoretical Community Ecology}{Graduate}{2009; 2011}{Allesina \& Dwyer}{}\vspace{-4.0mm}
    \cventry{ICTP Winter School on Quantitative Systems Biology: Quantitative Approaches in Ecosystem Ecology, Remote}{School}{2021}{Allesina, lecturer}{}\vspace{-4.0mm}
    \cventry{ICTP SAIFR School on Community Ecology, São Paulo, Brazil}{School}{2020}{Allesina, lecturer}{}\vspace{-4.0mm}
    \cventry{Mini course on Computing Skills for Biologists, Evóra, Portugal}{School}{2019}{Allesina}{}\vspace{-4.0mm}
    \cventry{Mini course BIOS 248 Scientific Computing for Ecologists, Stanford Universtity Hopkins Marine Station}{Graduate}{2015}{Allesina}{}\vspace{-4.0mm}
    \cventry{ICTP Spring College on the Physics of Complex Systems, Trieste, Italy}{School}{2014}{Allesina, lecturer}{}\vspace{-4.0mm}
    \cventry{São Paulo School on Ecological Networks, São Paulo, Brazil}{School}{2011}{Allesina, lecturer}{}\vspace{-4.0mm}
    \cventry{Biological Networks, University of Fribourg, Switzerland}{School}{2011}{Allesina, lecturer}{}\vspace{-4.0mm}
    \cventry{ICTP Theoretical Ecology and Global Change, Trieste, Italy}{School}{2009}{Allesina, lecturer}{}\vspace{-4.0mm}
    \cventry{Ecosystem Networks Modeling, University of Copenhagen, Denmark}{School}{2005--2006}{Allesina, lecturer}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{speaking}{%
\section{Speaking}\label{speaking}}

\begin{cventries}
    \cventry{Ecology \& Evolutionary Biology}{Princeton University, Princeton, NJ.}{}{Apr 6, 2023}{}\vspace{-4.0mm}
    \cventry{Ecology, Evolution and Behavior + Kellog Biological Station}{Michigan State University, East Lansing, MI.}{}{Oct 27-28, 2022}{}\vspace{-4.0mm}
    \cventry{Multiscale Microbial Communities workshop}{University of Chicago, Chicago, IL.}{}{Feb 22, 2022}{}\vspace{-4.0mm}
    \cventry{Department of Physics}{Washington University St. Louis, Remote.}{}{Nov 29, 2021}{}\vspace{-4.0mm}
    \cventry{Cross-cutting theories in biology}{University of Chicago + CNRS, Remote.}{}{May 29, 2021}{}\vspace{-4.0mm}
    \cventry{Ecology Live}{British Ecological Society, Remote.}{}{Feb 18, 2021}{}\vspace{-4.0mm}
    \cventry{Biomathematics Seminar}{Pennsylvania State University, Remote.}{}{Feb 9, 2021}{}\vspace{-4.0mm}
    \cventry{Department of Ecology and Evolutionary Biology}{Iowa State University, Remote.}{}{Feb 4, 2021}{}\vspace{-4.0mm}
    \cventry{Eco Seminars}{Eawag Dubendorf, Switzerland, Remote.}{}{Dec 19, 2020}{}\vspace{-4.0mm}
    \cventry{International Initiative for Theoretical Ecology Seminars}{Remote.}{}{Nov 24, 2020}{}\vspace{-4.0mm}
    \cventry{Biophysics Seminars}{Princeton University, Remote.}{}{Oct 19, 2020}{}\vspace{-4.0mm}
    \cventry{Department of Chemistry, Life Sciences and Environmental Sustainability}{Università di Parma, Italy}{}{June 28, 2019}{}\vspace{-4.0mm}
    \cventry{Department of Physics}{Università di Padova, Padua, Italy.}{}{June 27, 2019}{}\vspace{-4.0mm}
    \cventry{Biophysics Seminar}{Massachusetts Institute of Technology, Cambridge, MA.}{}{May 22, 2019}{}\vspace{-4.0mm}
    \cventry{Graduate Science Education Seminar}{Harvard Medical School, Boston, MA.}{}{May 21, 2019}{}\vspace{-4.0mm}
    \cventry{Center for Data and Computing}{University of Chicago, Chicago, IL.}{}{May 17, 2019}{}\vspace{-4.0mm}
    \cventry{Department of Epidemiology}{University of Florida, Gainesville, FA.}{}{May 2, 2019}{}\vspace{-4.0mm}
    \cventry{Department of Ecology \& Evolutionary Biology}{Yale University, New Haven, CT.}{}{Apr 3, 2019}{}\vspace{-4.0mm}
    \cventry{Stazione Zoologica Anton Dohrn}{Naples, Italy.}{}{Oct 7, 2018}{}\vspace{-4.0mm}
    \cventry{NetSci 2018 (Satellite)}{Paris, France.}{}{June 12, 2018}{}\vspace{-4.0mm}
    \cventry{Istituto Italiano di Cultura}{Chicago, IL.}{}{Feb 23, 2018}{}\vspace{-4.0mm}
    \cventry{EvMorph Seminar}{University of Chicago, Chicago, IL.}{}{Jan 25, 2018}{}\vspace{-4.0mm}
    \cventry{Department of Biology}{Georgia Institute of Technology, Atlanta, GA.}{}{Nov 16, 2017}{}\vspace{-4.0mm}
    \cventry{Biophysics Seminar}{Massachusetts Institute of Technology, Cambridge, MA.}{}{Oct 26, 2017}{}\vspace{-4.0mm}
    \cventry{Society for Industrial and Applied Mathematics}{Workshop on Network Science, Pittsburgh, PA. Plenary Speaker.}{}{Jul 13, 2017}{}\vspace{-4.0mm}
    \cventry{American Mathematical Society, Spring Central Sectional Meeting}{Bloomington, IN. Keynote Speaker}{}{Apr 1, 2017}{}\vspace{-4.0mm}
    \cventry{British Ecological Society Annual Meeting}{Liverpool UK. Keynote Speaker.}{}{Dec 14, 2016}{}\vspace{-4.0mm}
    \cventry{Science at the Edge}{Michigan State University, East Lansing, MI.}{}{Oct 27, 2016}{}\vspace{-4.0mm}
    \cventry{Computation in Science}{University of Chicago, Chicago IL.}{}{Oct 12, 2016}{}\vspace{-4.0mm}
    \cventry{Mathematical Biosciences Institute}{Columbus, OH.}{}{Apr 14, 2016}{}\vspace{-4.0mm}
    \cventry{Statistics Colloquium}{University of Chicago, Chicago, IL.}{}{Feb 29, 2016}{}\vspace{-4.0mm}
    \cventry{Wildlife Ecology and Conservation Seminars}{University of Florida, Gainesville, FL.}{}{Feb 1, 2016}{}\vspace{-4.0mm}
    \cventry{Santa Fe Institute}{Santa Fe, NM.}{}{Dec 11, 2015}{}\vspace{-4.0mm}
    \cventry{Department of Mathematics}{DePaul University, Chicago, IL.}{}{Nov 13, 2015}{}\vspace{-4.0mm}
    \cventry{Department of Biology}{Stanford University, Palo Alto, CA.}{}{Oct 8, 2015}{}\vspace{-4.0mm}
    \cventry{Living systems from interactions to critical behavior}{Venezia, Italy.}{}{Sept 18-19, 2015}{}\vspace{-4.0mm}
    \cventry{Ecological Society of America Annual Meeting}{Baltimore, MD. Contributed.}{}{Aug 14, 2015}{}\vspace{-4.0mm}
    \cventry{E3B seminar series}{ETH Zürich, Zurich, Switzerland.}{}{Mar 12, 2015}{}\vspace{-4.0mm}
    \cventry{6th Swedish Meeting in Mathematics in Biology}{Linköping, Sweden. Keynote Speaker}{}{Dec 5, 2014}{}\vspace{-4.0mm}
    \cventry{Ginzburg Colloquim}{Stony Brook University, Stony Brook, NY.}{}{Nov 5, 2014}{}\vspace{-4.0mm}
    \cventry{Computational Social Science Workshop}{University of Chicago, Chicago, IL.}{}{Oct 31, 2014}{}\vspace{-4.0mm}
    \cventry{Natural Resources \& Environmental Sciences}{U. Illinois at Urbana-Champaign, Urbana, IL.}{}{Sept 19, 2014}{}\vspace{-4.0mm}
    \cventry{Sci Foo}{Google, Mountain View, CA.}{}{Aug 10, 2014}{}\vspace{-4.0mm}
    \cventry{Bernoulli Lecture}{Center Interfacultaire Bernoulli, EPFL, Lausanne, Switzerland.}{}{July 10, 2014}{}\vspace{-4.0mm}
    \cventry{Marine Biological Lab}{Woods Hole, MA.}{}{May 5, 2014}{}\vspace{-4.0mm}
    \cventry{Graduate group in ecology}{University of California Davis, Davis, CA.}{}{Dec 5, 2013}{}\vspace{-4.0mm}
    \cventry{Food Webs Science for Impact}{Giessen, Germany. Keynote Speaker}{}{Nov 13, 2013}{}\vspace{-4.0mm}
    \cventry{Society of Population Ecology}{Sakai, Japan. Keynote Speaker}{}{Oct 12, 2013}{}\vspace{-4.0mm}
    \cventry{Department of Biology}{University of Puerto Rico – Rio Piedras, San Juan, Puerto Rico.}{}{Apr 22, 2013}{}\vspace{-4.0mm}
    \cventry{iDiv}{Leipzig, Germany. Invited}{}{Mar 14, 2013}{}\vspace{-4.0mm}
    \cventry{Martin School}{University of Oxford, Oxford, UK.}{}{Nov 1, 2012}{}\vspace{-4.0mm}
    \cventry{Department of Biology}{University of Umeå, Umeå, Sweden.}{}{Sept 24, 2012}{}\vspace{-4.0mm}
    \cventry{Theory group}{University of Michigan, Ann Arbor, MI.}{}{Sept 14, 2012}{}\vspace{-4.0mm}
    \cventry{NetSci 2012}{Evanston, IL. Invited}{}{June 23, 2012}{}\vspace{-4.0mm}
    \cventry{BioM\&S Symposium 2012}{University of Guelph, CA. Keynote speaker}{}{June 7, 2012}{}\vspace{-4.0mm}
    \cventry{Department of Ecology \& Evolution}{University of Chicago, Chicago IL.}{}{May 14, 2012}{}\vspace{-4.0mm}
    \cventry{Institute for Biodiversity and Ecosystem Dynamics}{University of Amsterdam, Amsterdam, the Netherlands. Keynote speaker}{}{Apr 26, 2012}{}\vspace{-4.0mm}
    \cventry{EEB Retreat}{University of Toronto, Toronto, Canada. Keynote speaker}{}{Apr 13, 2012}{}\vspace{-4.0mm}
    \cventry{Biology}{Case Western Reserve, Cleveland, OH.}{}{Apr 6, 2012}{}\vspace{-4.0mm}
    \cventry{Chicago Humanities Festival}{Chicago, IL. Invited}{}{Oct 23, 2011}{}\vspace{-4.0mm}
    \cventry{Biology}{University of Sao Paulo, Sao Paulo, Brazil. Invited}{}{Sept 15, 2011}{}\vspace{-4.0mm}
    \cventry{Biology}{University of Campinas, Brazil, Campinas, Brazil.}{}{Sept 14, 2011}{}\vspace{-4.0mm}
    \cventry{Ecology and Evolutionary Biology}{Iowa State University, Ames, IA.}{}{Sept 1 and 2, 2011}{}\vspace{-4.0mm}
    \cventry{Ecological Society of America Annual Meeting}{Austin, TX. Contributed.}{}{Aug 8, 2011}{}\vspace{-4.0mm}
    \cventry{International Environmetrics Society – Regional Meeting}{La Crosse, WI. Invited}{}{July 18, 2011}{}\vspace{-4.0mm}
    \cventry{European Conference on Ecological Modeling}{Riva del Garda, Italy. Contributed.}{}{June 2, 2011}{}\vspace{-4.0mm}
    \cventry{British Ecological Society Annual Meeting}{Leeds, UK. Invited}{}{Sept 7, 2010}{}\vspace{-4.0mm}
    \cventry{Dipartimento di Scienze Ambientali}{Università di Parma, Parma, Italy. Invited}{}{Jul 7, 2010}{}\vspace{-4.0mm}
    \cventry{1st Spark Reception Agent-based Modeling.}{University of Chicago, Chicago, IL. Invited}{}{Apr 29, 2010}{}\vspace{-4.0mm}
    \cventry{CSCS}{University of Michigan, Ann Arbor, MI. Invited}{}{Apr 22, 2010}{}\vspace{-4.0mm}
    \cventry{Bren School}{University of California Santa Barbara, Santa Barbara, CA.}{}{Feb 16, 2010}{}\vspace{-4.0mm}
    \cventry{Department of Biology}{University of Illinois at Chicago, Chicago, IL.}{}{Feb 2, 2010}{}\vspace{-4.0mm}
    \cventry{The Northwestern Institute on Complex Systems (NICO)}{Northwestern University, Evanston, IL.}{}{Dec 9, 2009}{}\vspace{-4.0mm}
    \cventry{NCEAS Ecolunch}{Santa Barbara, CA.}{}{Oct 9, 2009}{}\vspace{-4.0mm}
    \cventry{Ecological Society of America Annual Meeting}{Milwaukee, WI. Contributed.}{}{Aug 4, 2008}{}\vspace{-4.0mm}
    \cventry{NCEAS Ecolunch}{Santa Barbara, CA.}{}{May 5, 2008}{}\vspace{-4.0mm}
    \cventry{Department of Ecology \& Evolution}{University of Chicago, Chicago, IL. Invited}{}{April 16, 2008}{}\vspace{-4.0mm}
    \cventry{Early Career Scientists Symposium}{University of Michigan, Ann Arbor, MI. Invited}{}{March 15, 2008}{}\vspace{-4.0mm}
    \cventry{Ecological Society of America Annual Meeting}{San Jose, CA. Invited}{}{Aug 8, 2007}{}\vspace{-4.0mm}
    \cventry{Society for Mathematical Biology Annual Meeting}{San Jose, CA. Invited}{}{Aug 3, 2007}{}\vspace{-4.0mm}
    \cventry{Dipartimento di Scienze Ambientali}{Università di Parma, Parma, Italy. Invited}{}{Feb 20, 2007}{}\vspace{-4.0mm}
    \cventry{Niels Bohr Institute - Center for Models of Life}{Copenhagen, Denmark. Invited}{}{Feb 15, 2007}{}\vspace{-4.0mm}
    \cventry{Ecological Society of America Annual Meeting}{Memphis, TN. Contributed.}{}{Aug 9, 2006}{}\vspace{-4.0mm}
    \cventry{University of Copenhagen}{Copenhagen, Denmark. Invited}{}{Jun 7, 2006}{}\vspace{-4.0mm}
    \cventry{Dipartimento di Scienze Ambientali}{Università di Parma, Parma, Italy. Invited}{}{Jun 5, 2006}{}\vspace{-4.0mm}
    \cventry{Collegium Budapest, Institute for Advanced Study}{Budapest, Hungary. Invited}{}{May 26, 2006}{}\vspace{-4.0mm}
    \cventry{Chesapeake Biological Laboratory}{University of Maryland, Solomons, MD. Invited}{}{Nov 28, 2005}{}\vspace{-4.0mm}
    \cventry{Ecological Society of America Annual Meeting}{Montreal, Canada. Contributed}{}{Aug 9, 2005}{}\vspace{-4.0mm}
    \cventry{Fourth European Conference on Ecological Modelling}{Bled, Slovenia. Contributed}{}{Sept 29, 2004}{}\vspace{-4.0mm}
    \cventry{Peter Yodzis Colloquium}{University of Guelph, Guelph, Canada. Contributed}{}{Apr 24, 2004}{}\vspace{-4.0mm}
\end{cventries}


\label{LastPage}~
\end{document}
