---
name: Stefano
surname: Allesina
phone: +1 773 702 7825
www: stefanoallesina.github.io
email: "sallesina@uchicago.edu"
github: StefanoAllesina
googlescholar: "14DTOacAAAA"
researchgate: Stefano-Allesina
date: "`r format(Sys.time(), '%B %Y')`"
papersize: letter
header-includes:
   - \usepackage{soul}
   - \usepackage[backend=biber]{biblatex}
   - \usepackage{enumitem}
fontsize: 10
output:
  vitae::awesomecv: default
---

<!---
NOTE: 
For some reason, this only works with version 0.5.3 of package vitae
You can install it using:

install.packages("https://cran.r-project.org/src/contrib/Archive/vitae/vitae_0.5.3.tar.gz", repos = NULL, type = "source")

To compile CV just knit

--->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(tibble)
```

\colorlet{awesome}{awesome-emerald}
\colorlet{awesome}{awesome-nephritis}
\colorlet{awesome}{awesome-orange}

# Appointments

```{r, warning=FALSE, message=FALSE}
 read_csv("table_appointments.csv")%>% 
  detailed_entries(Department, Years, Title, Institution)
```

# Education
```{r, warning=FALSE, message=FALSE}
 read_csv("table_education.csv")%>% 
  detailed_entries(Area, Years, Degree, Institution, Advisor)
```

# Published articles

```{r}
library(dplyr)
bibliography_entries("papers.bib") %>%
  arrange(desc(issued), author)
```

# Preprints

```{r}
library(dplyr)
bibliography_entries("preprints.bib") %>%
  arrange(desc(issued), author)
```

# Books, book reviews & chapters

```{r}
library(dplyr)
bibliography_entries("books.bib") %>%
  arrange(desc(issued), author)
```

# Support
```{r, warning=FALSE, message=FALSE}
 read_csv("table_support.csv")%>% 
  detailed_entries(Title, Period, Agency, Money, PI)
```

# Mentoring
## Graduate students
Si Tang (2010-2013), Elizabeth Sander (2012-2017) (with J.T. Wootton), Matthew Michalska-Smith (2013-2018), Carlos Marcelo Serván (2016-2020), Zach Miller (2017-2022), Pablo Lechon-Alonso (2021-)

## Postdocs
Anna Eklöf (2010-2012), Phillip Staniczenko (2011-2013), Samraat Pawar (2012-2013), György Barabás (2014-2016), Madlen Wilmes (2015), Jacopo Grilli (2015-2017), Daniel Maynard (2017-2019), Srilena Kundu (2022-2024),  Paula Lemos-Costa (2019-2024)

## Undergraduate/predoctoral
Jose Rojas (2009-2010), Alex Zook (2009-2010), Philip Reinhold (2010-2011), M Moore (2010-2011), Jason Kopp (2011-2012), Matthew Smith (2012-2013), Michael Begun (2012-2013), Cody Weinberger (2013-2015), Theo Gibbs (2016-2018), Kevin Trickey (2017), Abby Skwara (2019-2021), Rukmini Harale (2025-)

# Awards & Membership
* U. Chicago Biological Sciences Division, Distinguished Investigator Award (2018).
* NSF CAREER Award (2012).
* NCEAS postdoctoral associate (2007, 2 years of support).
* Italian Ministry of University - PhD Scholarship (2002, 3 years of support).
* International Society for Ecological Modeling young researcher bursary (2004).
* Member of the Ecological Society of America (starting 2005).
* Member of the British Ecological Society (starting 2010).

# Service and leadership

## University of Chicago
* College Council (nominated) and Committee of the College Council (elected), 2024-
* Committee on Future Academic Directions in Climate and Energy, advising President Alivisatos and Provost Lee, 2022
* Chair, Ecology & Evolution, 2021-
* Director of Graduate Studies, Ecology & Evoltuion, 2014-2021
* Committee on Promotion and Tenure, 2015-2020
* Committee on Assistant Professors, 2014-2015

## Editor
* PLoS Computational Biology, Guest Editor (2012-2015), Associate Editor (2015-2017), Deputy Editor (2017-2021)
* Guest Editor for PNAS (2018), eLife (2015) 
* Scientific Reports, Editor (2015-2017)
* Journal of Complex Networks, Associate Editor (2012-2017)
* Faculty of 1000, Population Ecology, (2011-2016)
* Oikos, Subject Editor (2009-2017)

## Reviewer

American Naturalist; Basic and Applied Ecology; Behavioral Ecology; Biological Reviews; Biology Letters; BioScience; Branco Weiss Fellowship; Briefings in Bioinformatics; Chaos; Ecography; Ecological Complexity; Ecological Engineering; Ecological Indicators; Ecological Modelling; Ecological Monographs; Ecology; Ecology Letters; Environmental Modelling & Assessment; Environmental Modelling & Software; Estuarine, Coastal and Shelf Science; European Physical Journal B; European Research Council; Fisheries Research; Global Ecology and Biogeography; Journal of Animal Ecology; Journal of Mathematical Biology; Journal of Robust and Nonlinear Control; Journal of the Association for Information Science and Technology; Journal of Theoretical Biology; Journal of the Royal Society Interface; Marine Ecology Progress Series; Marsden Fund -- Royal Society of New Zealand; Methods in Ecology & Evolution; Microsoft Research; National Science Foundation; Nature; Nature Communications; Nature Ecology & Evolution; Nature Methods; Nature Physics; NERC; Oikos; Philosophical Transactions of the Royal Society Series B; Physical Reviews E; Physical Reviews X; Physics Letters A; PLoS Biology; PLoS Computational Biology; PLoS One; Proceedings of the National Academy of Sciences USA; Proceedings of the Royal Society Series B; Revue canadienne des sciences de l'information et de bibliotheconomie; Science; Science Advances; Scientometrics; Sinauer Publishing; The Social Science Journal; The Lancet Global Health; Theoretical Ecology; Theoretical Population Biology; The Quarterly Review of Biology; Romanian National Council for Scientific Research; Scientific Reports; Trends in Ecology & Evolution; Trends in Parasitology; U. California Press; U. Chicago Press; U. Nebraska Omaha Internal Funding.

## Panelist
National Science Foundation (EF 2010, GRFP 2016)

## Organizer
* ICTS-ICTP Winter School on Quantitative Systems Biology (S. Allesina, J. Grilli, A. Goyal and M. Krishnadas) 2025
* NITMB Workshop on Random Dynamical Systems, with Applications in Biology (S. Allesina, A. Auffinger, N. Chandramoorthy, B. Doiron and M. Silber) 2024
* NITMB Workshop on Ecological Dynamics of Microbial Communities: new approaches (S. Allesina, L.A. Nunes Amaral and S. Kuehn) 2024
* BSD Boot Camp on Quantitative Biology (S. Allesina, S. Palmer and V. Prince) 2015-2019
* A primer in ecological networks: theory & data (A. Bodini, G. DeLeo, S. Allesina & C. Bondavalli) 2008

# Teaching
```{r, warning=FALSE, message=FALSE}
 read_csv("table_teaching.csv")%>% 
  detailed_entries(Class, Instructors, Type, Years)
```

# Speaking
```{r, warning=FALSE, message=FALSE}
 read_csv("table_talks.csv")%>% 
  detailed_entries(What, Date, Location)
```
